Apparent preferences for cognitive effort fade when multiple forms of effort

### 2020-12-11 Cost_manuscript.Rmd
added model fitting procedure deets

  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm (Huys et al., 2011). Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution. Accordingly, a point estimate for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in the individual subject parameter estimates were calculated by taking the inverse of the Hessian matrix at the MAP estimate. Next, the mean of the prior was updated by taking the weighted mean of individual subject estimates, and the variance of the prior was updated by taking the weighted variance across the parameter estimates of individual subjects. This process was repeated until the mean and variance of the prior for all parameters converged (a change of less than .1% across successive iterations). Full mathematical details of the algorithm can be found in Huys et al., 2011, and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).

  Model comparison was performed by calculating Bayes Information Criterion at the group level (integrated BIC or iBIC; Huys et al., 2011; Kane et al., 2019). iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:

@@

  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Kane et al., 2019).

@@

  Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role. This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset. For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand. We therefore fixed each value of $c_{demand}$ (i.e. $c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted *a posteriori* distribution from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$. This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.

>>>>

  For each model, both population level and individual subject level parameters were fit simultaneously using an Expectation-Maximization algorithm [@Huys2011; @Huys2012]. Briefly, it was assumed that, at the population level, each parameter was distributed according to a Gaussian distribution, defined by a mean and standard deviation; the individual subject parameters were drawn from this distribution. Accordingly, a point estimate for the individual subject parameters were found via maximum a posteriori (MAP) estimation using the population distribution for each parameter as the priors, and the variance in the individual subject parameter estimates were calculated by taking the inverse of the Hessian matrix at the MAP estimate. Next, the mean of the prior was updated by taking the weighted mean of individual subject estimates, and the variance of the prior was updated by taking the weighted variance across the parameter estimates of individual subjects. This process was repeated until the mean and variance of the prior for all parameters converged (a change of less than .1% across successive iterations). Full mathematical details of the algorithm can be found in Huys et al. (2011, 2012), and the algorithm was implemented using a custom written R package, GaussExMax, available on github (github.com/gkane26/GaussExMax).

  Model comparison was performed by calculating Bayes Information Criterion at the group level [integrated BIC or iBIC; @Huys2011; @Huys2012; @Kane2019]. iBIC penalizes the likelihood of the data given model parameters $p(d | model)$ for model flexibility (the number of parameters, $k$), and the size of the penalty depends on the number of observations $o$:

@@

  A Laplace approximation was used to find the log marginal likelihood, the likelihood of the data for each subject given the population level distribution over each parameter (Huys et al., 2011; Huys et al., 2012; Kane et al., 2019).

@@

  Since participants in the between-subjects experiment experienced a single type of demand, the values of $c_{demand}$ and $C$ where the same and $\alpha_w$ did not play a role. This resulted in just fitting parameters $c_{demand}$ and $\beta$ for that dataset. For the within-subjects group, we assumed that the resulting $c_{demand}$ values from the first experiment reflected the actual bias induced by each demand. We therefore fixed each value of $c_{demand}$ (i.e. $c_{cognitive}$, $c_{wait}$, and $c_{physical}$) to the mean of the fitted parameters from each between-subjects demand group, and fit the global bias $C$, the convergence rate $\alpha_w$, and temprature $\beta$. This dynamic allowed for the observed merging of acceptances across demands in the within-subjects experiment, while respecting the stability in the between-subjects study.
